On the properties of projectile motion and quadratic air resistance

### 2016-03-17 Paper/main.tex
Minor

		x = \int u\,dt = \int \frac{u_0}{u_0kt+1}\,dt = u_0\,\int\frac{1}{u_0kt+1}\,dt
	Let $s = u_0kt+1 \implies \frac{ds}{dt} = u_0k \implies dt = \frac{ds}{u_0k}$.

@@

	We have derived the functions for projectile motion and determined some properties of it. These results are testable and exact under the conditions specified. We have developed analytical solutions to one dimensional air resistance and produced testable predictions which were tried in an experiment and no fundamental errors could be detected. The solutions were developed into two dimensions with approximations to keep the solutions purely analytical. These approximations were compared to numerical solutions and evaluated. While discrepancies could be found they were acceptable in size.

>>>>

		x &= \int u\,dt = \int \frac{u_0}{u_0kt+1}\,dt = u_0\,\int\frac{1}{u_0kt+1}\,dt\\\nonumber
	\mathrm{Let }\,s &= u_0kt+1 \implies \frac{ds}{dt} = u_0k \implies dt = \frac{ds}{u_0k}\\\nonumber

@@

	We have derived the equations of motion for projectile motion and determined some properties of it. These results are testable and exact under the conditions specified. We have developed analytical solutions to one dimensional quadratic air resistance and produced testable predictions which were tried in an experiment and no fundamental errors could be detected. The solutions were developed into two dimensions with approximations to keep the solutions purely analytical. These approximations were compared to numerical solutions and evaluated. While discrepancies could be found they were acceptable in size.
